Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-19 doc/report/discussion.tex
typos, and removed some red texts, also removed .pdf file..., compile the src when you need, don't include pdf file in it

\textbf{XBee:} The communication between XBees are complicated. For one, the signals are transmitted one by one instead of in a packet. Hence, we need to handle with extra care. In addition, sometimes multiple client can be sending signals simultaneously. We added a delay to each client that is proportional to their client IDs.

\textbf{Slider:} The slider we ordered is actually a soft potentiometer that returns a value between 0 to 1023 when pressure is applied to it. And the returned value reflects the position being pressed along the x-axis. To detect tap is easy. To detect hold, we need to handle accidentally release since the soft potentiometer requires certain amount of strength and the glass could move when the user is sliding along the temple. We also added a bounce handling so that the main program is only notified of slide change if a certain threshold of value is changed on the slider. Finally, we added the double tap gesture and it was a bit tricky to tell it from accidentally release. We believe that we could purchase a better piece in our next prototype so that we can concentrate more on the interaction design rather than the basic components.

>>>>

\textbf{XBee:} The communication between XBees are complicated. For one, the signals are transmitted one by one instead of in a packet. Hence, we need to handle with extra care. In addition, sometimes multiple clients can be sending signals simultaneously. We added a delay to each client that is proportional to their client IDs to avoid conflicts.

\textbf{Slider:} The slider we ordered is actually a soft potentiometer that returns a value between 0 to 1023 when pressure is applied to it. And the returned value reflects the position being pressed along the x-axis. To detect tap is easy. To detect hold, we need to handle accidentally release since the soft potentiometer requires certain amount of strength and the glass could move when the user is sliding along the temple. We also added a bounce handling so that the main program is only notified of slide change if a certain threshold of value is changed on the slider. Finally, we added the double tap gesture and it was a bit tricky to tell it from accidentally release. We believe that we could use a better piece
%purchase a better piece 
in our next prototype so that we can concentrate more on the interaction design rather than the basic components.

### 2013-05-19 doc/report/evaluation.tex
typos, and removed some red texts, also removed .pdf file..., compile the src when you need, don't include pdf file in it

\textcolor{red}{Will fill this evaluation when we get to it.}
Some of the ideas as to how to work on evaluation include: (A) Make a mobile (web) app that can remotely control the appliances through the gateway. Give a sequence of tasks to the tester and have him complete the tasks first on smartphone then use the Glass. (B) Observe the differences between using LED, Recon screen, and other feedbacks such as audio, and how that affects the user experience.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

%\textcolor{red}{Will fill this evaluation when we get to it.}
Constrained by the time within a semester, we haven't conducted a formal user study. Based on our discussions with the instructors, we have some initial plans as to how to work on evaluation -- (A) Make a mobile (web) app that can remotely control the appliances through the gateway. Give a sequence of tasks to the tester and have him complete the tasks first on smartphone then use the Glass. (B) Observe the differences between using LED, Recon screen, and other feedbacks such as audio, and how that affects the user experience.

We are planning to have evaluation done within the summer.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "main"
%%% End:

### 2013-05-19 doc/report/implementation.tex
update client image
remove some reminder texts
typos, and removed some red texts, also removed .pdf file..., compile the src when you need, don't include pdf file in it

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. We used Arduino Uno, which has an ATmega328 microcontroller and suffice our purpose in this project. We use off-the-shell IR receivers ({\color{red} confirm it is PNA4602}), which outputs 0V (low) on detection of 38 KHz carrier or 5V (high) otherwise. The XBee radio, accompanied with an XBee modems, takes charge of the communication with the Glass. LEDs are added as an indicator of the state of clients and visual feedback for users. Additional components are subject to the device being attached to. In our current system, we have a relay ({\color{red} need to know relay model}) which can control the AC power plug, and we have a USB connected computer to control video playing. The prototype is shown in Fig.\,\ref{fig:client}.

{\color{red} add clients photos here}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{../figs/client.jpg}
  \caption{Prototype of the clients}
  \label{fig:client}
\end{figure}

@@

{\color{red} add glass photos here}
\begin{figure}
  \centering
  \includegraphics[width=0.85\linewidth]{../figs/glass.png}
  \caption{Prototype of the Glass}
  \label{fig:glass}
\end{figure}

>>>>

\subsection{Clients}
The clients are comprised of a main Arduino board, an IR receiver, an XBee radio, and various actuators. We used Arduino Uno, which has an ATmega328 microcontroller and suffice our purpose in this project. We use off-the-shell IR receivers % ({\color{red} confirm it is PNA4602})
, which outputs 0V (low) on detection of 38 KHz carrier or 5V (high) otherwise. The XBee radio, accompanied with an XBee modems, takes charge of the communication with the Glass. LEDs are added as an indicator of the state of clients and visual feedback for users. Additional components are subject to the device being attached to. In our current system, we have a relay %({\color{red} need to know relay model}) 
which can control the AC power plug, and we have a USB connected computer to control video playing. The prototype is shown in Fig.\,\ref{fig:client}.

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{../figs/client.png}
  \caption{Prototype of the clients}
  \label{fig:client}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.85\linewidth]{../figs/glass.png}
  \caption{Prototype of the Glass}
  \label{fig:glass}
\end{figure}
